The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-06 talk/vmil2012/paper.tex
add spark line
this is "done"
this part is done too

\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[pdfpagelabels=true]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}

@@

\bigtodo{reviewer b: sadly no graphs}

@@

\bigtodo{reviewer c: Figure 7 was printed out of order. It was not clear if
    Figure 7 was talking about static measures (count once per compilation),
    vs. dynamic measures (count once per actual execution). When I have done
    studies like this in the past the difference between these two measures can
    be very interesting. One has more of an impact on memory and compiler
    issues, while the other will more significantly affect execution
    performance.
}

@@

%\section*{Appendix}
%\todo{remove this section and the figures}
%\begin{figure*}
%    \include{figures/ops_count_table}
%    \caption{Relative numbers of operations in the traces generated for
%    different benchmarks}
%    \label{fig:ops_count}
%\end{figure*}
%\begin{figure*}
%\centering
%\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
%\caption{Relative frequency of operations before and after optimization}
%\label{fig:ops_pie}
%\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\listoftodos
\end{document}

>>>>

\usepackage{ifthen}
\usepackage{sparklines}
\usepackage{booktabs}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[pdfpagelabels=true]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}

@@

@@

\bigtodo{reviewer c: Figure 7 was printed out of order.}

@@

%\section*{Appendix}

%\todo{remove this section and the figures}
%\begin{figure*}
%    \include{figures/ops_count_table}
%    \caption{Relative numbers of operations in the traces generated for
%    different benchmarks}
%    \label{fig:ops_count}
%\end{figure*}
%\begin{figure*}
%\centering
%\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
%\caption{Relative frequency of operations before and after optimization}
%\label{fig:ops_pie}
%\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\listoftodos
\end{document}
